 \documentclass[letterpaper,11pt]{amsart}
\textwidth=16.00cm 
\textheight=22.00cm 
\topmargin=0.00cm
\oddsidemargin=0.00cm 
\evensidemargin=0.00cm 
\headheight=0cm 
\headsep=0.5cm

\textheight=610pt

\usepackage{latexsym,array,delarray,amsthm,amssymb,epsfig}%eufrak
%\usepackage[sumlimits]{amsmath}

% \usepackage[centredisplay,PostScript=dvips]{diagrams}
%\usepackage[dvips]{color}
%\usepackage[mathscr]{eucal}mathrsfs

% Theorem Formatting Commands.
\theoremstyle{plain}
\newtheorem{thm}{Theorem}
%\newtheorem{lemma}{Lemma}[section]
\newtheorem{lemma}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}
\newtheorem*{thm*}{Theorem}
\newtheorem*{lemma*}{Lemma}
\newtheorem*{prop*}{Proposition}
\newtheorem*{cor*}{Corollary}
\newtheorem*{conj*}{Conjecture}

\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\newtheorem{ex}[thm]{Example}
\newtheorem{pr}{Problem}
\newtheorem{alg}[thm]{Algorithm}
\newtheorem{ques}[thm]{Question}

\theoremstyle{remark}
\newtheorem*{rmk}{Remark}
\newtheorem*{obs}{Observation}



\DeclareMathOperator{\gl}{GL}
\DeclareMathOperator{\aut}{Aut}



\begin{document}

\Large

\begin{center}
{\bf Math 7110 -- Homework  1 --  Due:  September 1, 2021}
\end{center}

\normalsize



\medskip

\noindent {\bf Practice Problems:}

\begin{pr}
    Show that an element in $S_n$ has order two if and only if it is a product of commuting cycles.
\end{pr}

\begin{pr}
    Show that $\gl_n(F)$ is non-abelian if $n \ge 2$.
\end{pr}

\begin{pr}
    Show that the following group is isomorphic to the dihedral group $D_4$
    \[
        \langle x,y | x^2=y^2=(xy)^2=1 \rangle.
    \]
\end{pr}

\begin{pr}
Make an appointment to visit me 
in my office sometime before 5 PM on Thursday, September 2.  I will pass around
a signup sheet for meetings on Monday, August 23rd.

Be prepared
to answer the following questions:
\begin{enumerate}
\item  Why are you taking this class and what do you hope to get out of it?
\item  What other math classes have you taken?
\item  What are your career goals after you graduate?
\end{enumerate}
\end{pr}

\bigskip

Type solutions to the following problems in \LaTeX, and email the tex and PDF files to me by 10am on the indicated date.
Please title them as [lastname].tex and [lastname].pdf.
When preparing your solutions, you must follow the rules as laid out in the course syllabus.

\vspace{.5cm}

\noindent {\bf Graded Problems:} 


\begin{pr}
    Answer the following questions:
    \begin{enumerate}
        \item If $\phi: G\rightarrow H$ is an isomorphism, prove that $|\phi(x)| = |x|$ for all $x \in G$.
        \item Is the result true if $\phi$ is just a homomorphism? Prove or give a counterexample.
        \item Given $x \in S_n$, show that $|x|$ is the least common multiple of the lengths of the cycles in its cycle decomposition.
        \item Are $S_4$ and $D_{24}$ isomorphic? Why or why not?
    \end{enumerate}
\end{pr}

\begin{pr}
    Let $G$ be a group and let $\aut(G)$ be the set of all isomorphisms from $G$ onto $G$.
    \begin{enumerate}
        \item Prove that $\aut(G)$ is a group under function composition.
        \item Let $G$ be a finite group and let $\sigma \in \aut(G)$ be such that $\sigma(g) = g$ if and only if $g = 1$. If $\sigma^2$ is the identity map, prove that $G$ is abelian.
    \end{enumerate}
\end{pr}








\end{document}