 \documentclass[letterpaper,11pt]{amsart}
\textwidth=16.00cm 
\textheight=22.00cm 
\topmargin=0.00cm
\oddsidemargin=0.00cm 
\evensidemargin=0.00cm 
\headheight=0cm 
\headsep=0.5cm

\textheight=610pt

\usepackage{latexsym,amsthm,amssymb,epsfig,url}%eufrak
%\usepackage[sumlimits]{amsmath}

% \usepackage[centredisplay,PostScript=dvips]{diagrams}
%\usepackage[dvips]{color}
%\usepackage[mathscr]{eucal}mathrsfs

% Theorem Formatting Commands.
\theoremstyle{plain}
\newtheorem{thm}{Theorem}
%\newtheorem{lemma}{Lemma}[section]
\newtheorem{lemma}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}
\newtheorem*{thm*}{Theorem}
\newtheorem*{lemma*}{Lemma}
\newtheorem*{prop*}{Proposition}
\newtheorem*{cor*}{Corollary}
\newtheorem*{conj*}{Conjecture}

\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\newtheorem*{defn*}{Definition}
\newtheorem{ex}[thm]{Example}
\newtheorem{pr}{Problem}
\newtheorem{alg}[thm]{Algorithm}
\newtheorem{ques}[thm]{Question}

\theoremstyle{remark}
\newtheorem*{rmk}{Remark}
\newtheorem*{obs}{Observation}

\usepackage{color}
\newcommand{\dbfeedback}[1]{{\color{red} DB Feedback: #1}}

\newcommand{\conv}{{\rm Conv}}
\newcommand{\aff}{{\rm Aff}}



\begin{document}

\Large

\begin{center}
{\bf Math 7760 -- Homework  1 --  Due:  August 31, 2022}
\end{center}

\normalsize


\medskip

\noindent {\bf Practice Problems:}

\begin{pr}
    Show that every compact convex set has an extreme point. Give an example of a non-compact convex set with an extreme point.
\end{pr}


\begin{pr}
    Prove that $x \in \aff(x_1,\dots,x_n)$ if and only if
    \[
        \begin{pmatrix}
            1 \\
            x
        \end{pmatrix}
        \in
        \mathbb{R}\begin{pmatrix}
            1 & 1 & \dots & 1 \\
            x_1 & x_2 & \dots & x_n
        \end{pmatrix}
    \]
    and that $x \in \conv(x_1,\dots,x_n)$ if and only if
    \[
        \begin{pmatrix}
            1 \\
            x
        \end{pmatrix}
        \in
        \mathbb{R}_{\ge 0} \begin{pmatrix}
            1 & 1 & \dots & 1 \\
            x_1 & x_2 & \dots & x_n
        \end{pmatrix}
    \]
\end{pr}
\begin{pr}
    Let $X,Y \subseteq \mathbb{R}^d$ with $|X| = |Y| = d+1$.
    Assume $X,Y$ are each affinely independent sets.
    Prove that $\conv(X)$ and $\conv(Y)$ are affinely isomorphic.
\end{pr}



\bigskip

Type solutions to the following problems in \LaTeX, and email the tex and PDF files to me at \url{dbernstein1@tulane.edu} on the due date.
Please title them as [lastname].tex and [lastname].pdf.
When preparing your solutions, you must follow the rules as laid out in the course syllabus.

\vspace{.5cm}

\noindent {\bf Problems to write up:}

\begin{pr}
    Let $P,Q \subset \mathbb{R}^2$ be two-dimensional polytopes (i.e.~polygons).
    For each of the following statements, either prove that they are true, or provide a counterexample.
    \begin{enumerate}
        \item If $P$ and $Q$ have the same number of edges, then they are affinely isomorphic.
        \item If $P$ and $Q$ have the same number of edges, then they are combinatorially isomorphic.
        \item If $P$ and $Q$ are both triangles, then they are affinely isomorphic.
        \item If $P$ is a square and $Q$ is a parallelogram, then $P$ and $Q$ are affinely isomorphic.
        Begin by convincing yourself that it makes no difference if you assume that the vertices of $P$ are $\{0,1\}^2$ and that
        $(0,0)$ is a vertex of $Q$.
    \end{enumerate}
\end{pr}

\begin{pr}
    If you haven't taken a class with me yet, stop by my office hours.
    Be prepared to answer the following questions:
    \begin{enumerate}
        \item Why are you taking this class and what do you hope to get out of it?
        \item What other math classes have you taken?
        \item What are your career goals for after you graduate?
    \end{enumerate}
\end{pr}







\end{document}