 \documentclass[letterpaper,11pt]{amsart}
\textwidth=16.00cm 
\textheight=22.00cm 
\topmargin=0.00cm
\oddsidemargin=0.00cm 
\evensidemargin=0.00cm 
\headheight=0cm 
\headsep=0.5cm

\textheight=610pt

\usepackage{latexsym,amsthm,amssymb,epsfig,url}%eufrak
%\usepackage[sumlimits]{amsmath}

% \usepackage[centredisplay,PostScript=dvips]{diagrams}
%\usepackage[dvips]{color}
%\usepackage[mathscr]{eucal}mathrsfs

% Theorem Formatting Commands.
\theoremstyle{plain}
\newtheorem{thm}{Theorem}
%\newtheorem{lemma}{Lemma}[section]
\newtheorem{lemma}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}
\newtheorem*{thm*}{Theorem}
\newtheorem*{lemma*}{Lemma}
\newtheorem*{prop*}{Proposition}
\newtheorem*{cor*}{Corollary}
\newtheorem*{conj*}{Conjecture}

\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\newtheorem{ex}[thm]{Example}
\newtheorem{pr}{Problem}
\newtheorem{alg}[thm]{Algorithm}
\newtheorem{ques}[thm]{Question}

\theoremstyle{remark}
\newtheorem*{rmk}{Remark}
\newtheorem*{obs}{Observation}



\DeclareMathOperator{\gl}{GL}
\DeclareMathOperator{\aut}{Aut}



\begin{document}

\Large

\begin{center}
{\bf Math 7110 -- Homework  2 --  Due:  September 22, 2021}
\end{center}

\normalsize



\medskip

\noindent {\bf Practice Problems:}

\begin{pr}
    Section 3.2, questions 14 and 15 (recall that if $G$ acts on $S$ and $s \in S$, then the \emph{stabilizer} of $i$ is the subgroup $H$ of $G$ such that $hs = s$ for all $h \in H$).
\end{pr}

\begin{pr}
    Section 3.2, questions 16 and 22.
\end{pr}

\bigskip

Type solutions to the following problems in \LaTeX, and email the tex and PDF files to me at \url{dbernstein1@tulane.edu} by 10am on the indicated date.
Please title them as [lastname].tex and [lastname].pdf.
When preparing your solutions, you must follow the rules as laid out in the course syllabus.

\vspace{.5cm}

\noindent {\bf Graded Problems:} 

\begin{pr}
The center of a group $G$ is the set $Z(G) = \{ z \in G : gz = zg \mbox{ for all } g \in G\}$.
\begin{enumerate}
\item  Show that $Z(G)$ is a normal subgroup of $G$.
\item  Show that $Z(G) = G$ if and only if $G$ is abelian.
\item  Determine the center of the dihedral group $D_n$ for all $n$.
\item  Show that $G/Z(G)$ is a cyclic group if and only if $G$ is abelian.
\end{enumerate}
\end{pr}

\begin{pr}
    In this problem, you will prove the fundamental group theory result known as \emph{Lagrange's theorem}:
    if $H$ is a subgroup of $G$ and $G$ is finite, then $|H|$ divides $|G|$.
    \begin{enumerate}
        \item Let $H$ be a group acting on a set $A$. Let $\sim$ be the relation on $A$ given by
            \[
                a \sim b \qquad \textnormal{if and only if} \qquad a = hb \qquad \textnormal{for some } h \in H.
            \]
            Prove that $\sim$ is an equivalence relation.
            The equivalence class of $a \in A$ under $\sim$ is called the \emph{orbit} of $a$ under $H$.
        \item Now, let $H$ be a subgroup of a finite group $G$ and let $H$ act on $G$ by left multiplication.
            Let $\mathcal{O}$ be the orbit of some $x \in G$.
            Prove that the map
            \[
                H\rightarrow \mathcal{O} \qquad \textnormal{given by} \qquad h \mapsto hx
            \]
            is a bijection. Now prove that $|H|$ divides $|G|$ and that $H$ has $\frac{|G|}{|H|}$ left cosets in $G$.
    \end{enumerate}
\end{pr}






\end{document}