 \documentclass[letterpaper,11pt]{amsart}
\textwidth=16.00cm 
\textheight=22.00cm 
\topmargin=0.00cm
\oddsidemargin=0.00cm 
\evensidemargin=0.00cm 
\headheight=0cm 
\headsep=0.5cm

\textheight=610pt

\usepackage{latexsym,amsthm,amssymb,epsfig,url}%eufrak
%\usepackage[sumlimits]{amsmath}

% \usepackage[centredisplay,PostScript=dvips]{diagrams}
%\usepackage[dvips]{color}
%\usepackage[mathscr]{eucal}mathrsfs

% Theorem Formatting Commands.
\theoremstyle{plain}
\newtheorem{thm}{Theorem}
%\newtheorem{lemma}{Lemma}[section]
\newtheorem{lemma}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}
\newtheorem*{thm*}{Theorem}
\newtheorem*{lemma*}{Lemma}
\newtheorem*{prop*}{Proposition}
\newtheorem*{cor*}{Corollary}
\newtheorem*{conj*}{Conjecture}

\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\newtheorem*{defn*}{Definition}
\newtheorem{ex}[thm]{Example}
\newtheorem{pr}{Problem}
\newtheorem{alg}[thm]{Algorithm}
\newtheorem{ques}[thm]{Question}

\theoremstyle{remark}
\newtheorem*{rmk}{Remark}
\newtheorem*{obs}{Observation}

\usepackage{color}
\newcommand{\dbfeedback}[1]{{\color{red} DB Feedback: #1}}



\DeclareMathOperator{\gl}{GL}
\DeclareMathOperator{\aut}{Aut}



\begin{document}

\Large

\begin{center}
{\bf Math 7110 -- Homework  6 --  Due:  November 1, 2021}
\end{center}

\normalsize


\medskip

\noindent {\bf Practice Problems:}

\begin{pr}
    All the problems you missed on the test.
\end{pr}

\begin{defn*}
    Let $R$ be a ring and let $I,J$ be ideals of $R$. Define $IJ$ to be the ideal generated by $\{fg: f \in I, g \in J\}$
    and $I + J$ to be the ideal in $R$ generated by $\{f + g : f \in I, g \in J\}$.
\end{defn*}

\begin{pr}
    Let $R$ be a ring and let $I,J\subseteq R$ be ideals. 
    \begin{enumerate}
        \item Is $I + J$ always equal to $\{f+g:f \in I, g \in J\}$? Is $IJ$ always equal to $\{fg : f \in I, g \in J\}$?
        \item Prove that $I\cap J$ is an ideal containing $IJ$.
        \item Let $I = (2,x) \subseteq \mathbb{Z}[x]$ and use this to show that the containment in the previous part may not be strict.
        \item Prove that if $R$ is commutative and $I+J=R$ then $IJ = I\cap J$.
    \end{enumerate}
\end{pr}

\noindent {\bf Test practice:}

\begin{pr}
    Determine whether or not $2\mathbb{Z}$ and $3\mathbb{Z}$ are isomorphic as rings.
\end{pr}

\begin{pr}
    Dummit and Foote 7.3 question 10.
\end{pr}


\bigskip

Type solutions to the following problems in \LaTeX, and email the tex and PDF files to me at \url{dbernstein1@tulane.edu} by 10am on the due date.
Please title them as [lastname].tex and [lastname].pdf.
When preparing your solutions, you must follow the rules as laid out in the course syllabus.

\vspace{.5cm}

\noindent {\bf Graded Problems:}

\begin{pr}
    Dummit and Foote 7.3 question 17.
\end{pr}


\begin{pr}
    Dummit and Foote 7.3 questions 26 and 28.
\end{pr}


\end{document}